Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-27 review_article.Rmd
interactivity section headings

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(g1), 0, .5, 0.5, 0.45) +
  draw_plot(rasterGrob(g2), 0.5, 0.5, 0.5, 0.45) +
  draw_plot(rasterGrob(g3), 0.0, 0.0, 0.5, 0.45) +
  draw_plot(rasterGrob(g4), 0.5, 0, 0.5, 0.45) +
  draw_plot(usa_legend, 0, 0, 1, 0.1) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

@@

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(aus1), 0, .55, 0.5, 0.45) +
  draw_plot(rasterGrob(aus2), 0.5, 0.55, 0.5, 0.45) +
  draw_plot(rasterGrob(aus3), 0.0, 0.1, 0.5, 0.45) +
  draw_plot(rasterGrob(aus4), 0.5, 0.1, 0.5, 0.45) +
  draw_plot(aus_legend, 0, 0, 1, .1) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

@@

# Interactivity and Animation  {#ch:interacting}

@@

## Interactivity

@@

>>>>

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(g1), 0, .5, 0.5, 0.55) +
  draw_plot(rasterGrob(g2), 0.5, 0.5, 0.5, 0.55) +
  draw_plot(rasterGrob(g3), 0.0, 0.0, 0.5, 0.55) +
  draw_plot(rasterGrob(g4), 0.5, 0, 0.5, 0.55) +
  draw_plot(usa_legend, 0, 0, 1, 0.1) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

@@

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(aus1), 0, .55, 0.5, 0.55) +
  draw_plot(rasterGrob(aus2), 0.5, 0.55, 0.5, 0.55) +
  draw_plot(rasterGrob(aus3), 0.0, 0.1, 0.5, 0.55) +
  draw_plot(rasterGrob(aus4), 0.5, 0.1, 0.5, 0.55) +
  draw_plot(aus_legend, 0, 0, 1, .1) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

@@

# User interaction with maps  {#ch:interacting}

@@

## Interaction and animation in publicly available atlases

@@

## Under-utilised techniques
